---
title: "131_HW1"
author: "Zack Reardon"
date: "9/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 1.

Supervised learning refers to the process in which a program is trained to fit a model utilizing datasets containing both predictor variables and the response. Unsupervised learning refers to the process where a program trains itself utilizing data where only the predictors are present. The difference between supervised and unsupervised learning is that the data utilized in supervised learning is already labeled while the data used in unsupervised learning is not labeled.

Question 2.

A regression model is useful for modelling data where the response variable is quantitative while a classification model is useful for modelling data where the response variable is qualitative.

Question 3.

Two commonly used metrics for regression machine learning problems are Training MSE and Test MSE. Two commonly used metrics for classification machine learning problems are Training error rate and Test error rate.

Question 4.

Descriptive models, according to lecture 1, are models used to best visually emphasize a trend in data, such as a line on a scatterplot. Inferential models, according to lecture 1, are aimed to test theories and to state the relationship between response and predictors. Predictive models, according to lecture 1, are intended to predict the response variable with the lowest possible reducible error.

Question 5.

Mechanistic models, according to lecture 1, assume a parametric form, won't match the true unknown function f, and are based on a theory. Empirically-driven models, on the other hand, do not include any assumptions about the function f and are formed off of studied data. According to lecture 1, empirically-driven models are much more flexible by default then mechanistic models and are overfitting by nature. Mechanistic and empirically-driven models are similar in that they can be overfitted and can be made increasingly flexible. In general, a mechanistic model is easier to understand since the parametric assumption results in a simpler model. The bias-variance tradeoff is related to the use of mechanistic or empirically-driven models since each method may perform differently in terms of flexibility and interpretability.

Question 6.

The first question is predictive since it aims to predict the likelihood of an individual voting for a candidate, represented by the response variable Y. The second question is predictive since it aims to determine the relationship between the predictor (contact with candidate) and the response (voting for a particular candidate).

Exercise 1.

```{r}
library(tidyverse)
library(ggplot2)
ggplot(mpg, aes(x=hwy))+geom_histogram()
```

The highway mpgs of the cars in the mpg dataset tend to be clustered around approximately 17 and 26 miles per gallon.

Exercise 2.

```{r}
ggplot(mpg, aes(x=hwy, y=cty)) + geom_point()
```

There appears to be a strong linear relationship between hwy and cty meaning that there is a strong correlation between a car's highway and city mpg in the cars studied.

Exercise 3.

```{r}
ggplot(mpg, aes(x=reorder(manufacturer, manufacturer, function(x)-length(x)))) + geom_bar() + coord_flip() + xlab("manufacturer")
```

Dodge produced the most cars and Lincoln produced the least.

Exercise 4.

```{r}
ggplot(mpg, aes(x=hwy)) + geom_boxplot() + facet_wrap(~cyl, ncol=4)
```

It appears that cars with fewer cylinders will generally get better mpg on the highway.

Exercise 5.

```{r}
library(corrplot)
M=cor(mpg)
corrplot(mpg, method = 'number')
```
